Human Factors Influencing Visual Statistical Inference

### 2013-06-14 sociology_paper.tex
subject specific demographic variables

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{learning_trend.pdf} 
    \includegraphics[width=6.5in]{learning_trend_subject.pdf} 
   \caption{ Mean residuals of proportion correct obtained from the model \eqref{eqn:trend_response} fitted without attempt are plotted against attempt. Linear regression lines fitted through the points are shown. None of the slopes in these three experiments are statistically significant.}
   \label{fig:learning_trend_response}
\end{figure}

@@

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{learning_trend_time.pdf}    
 \includegraphics[width=6.5in]{learning_trend_time_subject.pdf}    
   \caption{ Mean residuals of log(time taken) obtained from model \eqref{eqn:trend_time} fitted without covariate attempt plotted against attempt. Linear regression lines are fitted through the points excluding the first attempt. For all the three experiments the downward slopes are statistically significant which indicates that MTurk workers take less time as they progress through their attempts.}
   \label{fig:learning_trend_time}
\end{figure}

@@

Observer demographics seem to have significant influence on performance in time taken to evaluate a lineup. Some variation is observed in terms of probability of correct evaluation. Age group 36-40, Countries other than India and United states, People who have a graduate degree appear to have significantly more probability to evaluate a lineup correctly. Gender does not have any effect on performance.

Individual learning trend is observed in both time taken and observer performance. But the overall performance of human observers does not increase through successive attempts while evaluating multiple lineups. The skill in evaluating the lineup in shorter time gets improved over successive evaluations. The earlier evaluations take significantly longer than the later evaluations. This result is very important as it suggests that the power estimated for visual inference using human subject experiment is robust and may not change if those participants are allowed to give feedback again. This investigation suggest that the skilled person may only do it faster.

>>>>

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{learning_trend.pdf} 
    \includegraphics[width=6.5in]{learning_trend_subject.pdf} 
   \caption{ Mean residuals of proportion correct obtained from the model \eqref{eqn:trend_response} fitted without attempt are plotted against attempt. Linear regression lines fitted through the points are shown. None of the slopes in these three experiments are statistically significant. Subject specific variations in the slopes are observed where some of the observers did worse and some did better over the successive attempts.}
   \label{fig:learning_trend_response}
\end{figure}

@@

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{learning_trend_time.pdf}    
 \includegraphics[width=6.5in]{learning_trend_time_subject.pdf}    
   \caption{ Mean residuals of log(time taken) obtained from model \eqref{eqn:trend_time} fitted without covariate attempt plotted against attempt. Linear regression lines are fitted through the points excluding the first attempt. For all the three experiments the downward slopes are statistically significant which indicates that MTurk workers take less time as they progress through their attempts. But subject specific variations in slopes are also observed where some of the subjects did worse over successive attempts while others did better.}
   \label{fig:learning_trend_time}
\end{figure}

@@

Observer demographics seem to have significant influence on performance in time taken to evaluate a lineup. Some variations among the factors are observed in terms of probability of correct evaluation. Age group 36-40, Countries other than India and United states, People who have a graduate degree appear to have significantly more probability to evaluate a lineup correctly. Gender does not have any effect on performance.

Individual learning trend is observed in both time taken and observer performance. Some individuals improved the performances while others showed decrease in their performances over attempts. But the overall performance of human observers does not increase through successive attempts while evaluating multiple lineups. The skill in evaluating the lineup in shorter time gets improved over successive evaluations. The earlier evaluations take significantly longer than the later evaluations. This result is very important as it suggests that the power estimated for visual inference using human subject experiment is robust and may not change if those participants are allowed to give feedback again. This investigation suggest that the skilled person may only do it faster.
